---
title: "MAP_onlymacro"
author: "Benthe Van Buyten"
date: "2025-08-06"
output: 
  html_document:
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_float: yes
    code_folding: hide
  word_document:
    toc: yes
  pdf_document:
    toc: yes
subtitle: MiCoS
---

# INTRODUCTION

Add some information on this macroplastics. 
This script is made to analyse the data of the counts of the macromaterials of the 240 fields sampled across the Benelux. 
Variables: 

- Counts per field of every litter category
- Total_macromaterial per hectare
- Total_onlymacro_plastic per hectare

```{r}
# Load packages
library(ggplot2)
library(readr)
library(dplyr)
library(stringr)
library(paletteer)
library(tidyr)
library(reshape2)
library(fastDummies)
library(patchwork)
library(MASS)
library(car)
library(emmeans)
library(multcomp)
library(multcompView)
```

# DATA SETUP

## Load data
```{r}
# Locate data
path <- ("./")

# Create full pathways to necessary data files
path_MAP_macro <- file.path(path, "MAP_onlymacro_Rfile_woOutliers.csv")

## Check if paths exists
file.exists(path_MAP_macro)

# Load data
MACRO <- read.csv(path_MAP_macro, sep = ";")
head(MACRO)
```

###Dataset mean of categories


```{r}
# Locate data
path <- ("./")

# Create full pathways to necessary data files
path_Mean_macro <- file.path(path, "Mean_onlymacro_woOutliers.csv")

## Check if paths exists
file.exists(path_Mean_macro)

# Load data
MAP_mean_categories_macro <- read.csv(path_Mean_macro, sep = ";")
head(MAP_mean_categories_macro)
```


**How many fields do not have any macroplastics**

On 8 fields no litter was found due to circumstances:

- MC24_023: Field was ploughed, therefore no litter could be found according to the sampling book.
- MC24_034: According to the sampling book, no litter was found due to snow and grass.
- MC24_037: Empty bag, Sampling book stated: A lot of snow on the field, not possible to find MaP
- MC24_127: Empty bag, according to sampling book: no MaP found due to high grass +- 30 cm
- MC24_216: Excluded for forgetting to note where the MaP were taken, no coordinates
- MC24_222: Empty bag due to grass
- MC24_223: Empty bag, no MaP found due to rapeseed
- MC24_235: Empty bag, no MaP found due to rapeseed

The fields above are excluded from the dataset.

On 7 fields no macrolitter was found:

- MC24_029: Empty bag, according to sampling book: only shells were found
- MC24_053: Empty bag, according to sampling book: no MaP contamination sources found, nothing stated about the MaP
- MC24_088: Empty bag, according to sampling book: no MaP contamination sources found, nothing stated about the MaP
- MC24_129: Empty bag, according to sampling book: no MaP found
- MC24_190: Empty bag, according to sampling book: Nothing stated about MaP
- MC24_191: According to the sampling book, Strobalen met folie rond en op de weg, plastic restanten maar nu niets op het veld te zien.
- MC24_212: No macrolitter found, only mesolitter
- MC24_217: Empty bag, according to sampling book: Nothing stated about MaP

The fields above are included in the dataset

On 7 fields, no macroplastic was found but other macromaterials were found:

- MC24_005
- MC24_014
- MC24_063
- MC24_114
- MC24_138: no macroplastic was found
- MC24_162
- MC24_175
- MC24_219

Three fields are see as outliers as the sampled surface was smaller compared to other fields :

- MC24_018 (207 000 plastics/Ha) 4 m^2
- MC24_073 (108 750 plastic/Ha) 16 m^2
- MC24_012 (44 000 plastics/Ha) 10 m^2

### Log Total Macromaterials and total macroplastics
Log10 nemen van macromaterials and macroplastics
If the value of macromaterials/macroplastics equals zero, we will do +1 because log10(1) = 0
```{r}
# NOG AAN TE PASSEN
# Data manipulatie
MACRO_all <- MACRO %>%
  
  # Data manipulation
  mutate(log_Total_macrolitter = log10(if_else(Total_onlymacro_material == 0, Total_onlymacro_material + 1, Total_onlymacro_material)), #Log10 of total_macromaterials, but if total_macromaterials is zero add +1 because log10(1) = 0.
         log_Total_macroplastic = log10(if_else(Total_onlymacro_plastic == 0, Total_onlymacro_plastic + 1, Total_onlymacro_plastic)), #Log10 of Total_onlymacro_plastics, but if Total_onlymacro_plastics is zero add +1 because log10(1) = 0.
         log_Total_macrometal = log10(if_else(Total_onlymacro_metals == 0, Total_onlymacro_metals + 1, Total_onlymacro_metals)),
         log_Total_macrorubber = log10(if_else(Total_onlymacro_rubber == 0, Total_onlymacro_rubber + 1, Total_onlymacro_rubber)),
         log_Total_macroglass = log10(if_else(Total_onlymacro_glass == 0, Total_onlymacro_glass + 1, Total_onlymacro_glass)),
         log_Total_macroNP = log10(if_else(Total_onlymacro_NaturP == 0, Total_onlymacro_NaturP + 1, Total_onlymacro_NaturP)),
         log_Total_macromis = log10(if_else(Total_onlymacro_mis == 0, Total_onlymacro_mis + 1, Total_onlymacro_mis)),
         log_Total_macroceramics = log10(if_else(Total_onlymacro_Ceramics == 0, Total_onlymacro_Ceramics + 1, Total_onlymacro_Ceramics)),
         log_Total_macrocount = log10(if_else(Total_onlymacro_material_count == 0, Total_onlymacro_material_count + 1, Total_onlymacro_material_count)),
         log_Total_macroplasticcount = log10(if_else(Total_onlymacro_plastic_count == 0, Total_onlymacro_plastic_count + 1, Total_onlymacro_plastic_count))
  )
```

## Bewerkingen NA
Uitfilteren van NA in de bewerkingen (compost, manure, tillage, Irrigation, pesticides, Usage_plastic_foil and crop_rotation)

Hiervan elk een aparte dataset maken aangezien de velden waarbij het is ingevuld niet 100% overeen komen:

- Compost: 28 velden NA
- Manure: 28 velden NA
- Irrigation: 29 velden NA veld MC030 extra tov compost and manure
- Tillage: 33 velden NA: MC030, 138, 160, 172, 146
- Crop-rotation: 26 velden NA
- Pesticides: 28 velden NA
- Crop rotation

```{r}
# Data manipulatie
MACRO_all_noNA <- MACRO_all %>%
  
  filter(!is.na(Compost), 
         !is.na(Manure), 
         !is.na(Irrigation), 
         !is.na(Usage_plastic_foil), 
         !is.na(tillage), 
         !is.na(crop_rotation), 
         !is.na(pesticides)) #NA uitfilteren

```

## Dataframe Belgium

```{r}
MACRO_Belgium <- MACRO_all %>%
  filter(Country == "Belgium")

MACRO_Belgium_noNA <- MACRO_Belgium %>%
  filter(!is.na(distance_city), 
         !is.na(distance_highway), 
         !is.na(distance_industrie_VL), 
         !is.na(distance_industrie_WL), 
         !is.na(distance_village), 
         !is.na(distance_waste_industriel_WL), 
         !is.na(min_distance_waste),
         !is.na(distance_waste_industriel_WL),
         !is.na(min_distance_industry))
```


## OMZETTING VAN LONG TO WIDE FORMAT

```{r}
# From long to wide 
##From long to wide format  (all)                     
MACRO_long <- MACRO_all %>%
  
  pivot_longer(
    cols = matches("^[A-G]\\d+$"),
    names_to = "waste_category",
    values_to = "counts"
  )

```

```{r}
# Focus only on the plastics
## Create a factor containing the order of plastic_category
order_plastic_category <- c(paste0("A", 1:21))

## Filter out only the plastics and remove samples with any zeroes from total plastics
MACRO_plastic_long <-  MACRO_long %>%
  
  filter(Total_onlymacro_plastic > 0,
         str_detect(waste_category, "A")) %>%

  # Adjust the factor level
  mutate(waste_category = factor(waste_category, levels = order_plastic_category))
```

```{r}
#MOEST JE DIT NODIG HEBBEN
# Voeg een nieuwe kolom toe met de details van de verschillende categoriën
MACRO_long <- MACRO_long %>%
  mutate(details = case_when(
    grepl("A1", waste_category) ~ "Bottle",
    grepl("A2", waste_category) ~ "Sheet",
    grepl("A3", waste_category) ~ "Bag",
    grepl("A4", waste_category) ~ "Caps and lids",
    grepl("A5", waste_category) ~ "Monofilament",
    grepl("A6", waste_category) ~ "Entangled monofilament",
    grepl("A7", waste_category) ~ "Synthetic rope",
    grepl("A8", waste_category) ~ "Plastic (animal) tags",
    grepl("A9", waste_category) ~ "Cable ties",
    grepl("A10", waste_category) ~ "Strapping band",
    grepl("A11", waste_category) ~ "Crates and containers",
    grepl("A12", waste_category) ~ "Sanitary products",
    grepl("A13", waste_category) ~ "Plastic construction material",
    grepl("A14", waste_category) ~ "Other",
    grepl("A15", waste_category) ~ "Medical related plastic",
    grepl("A16", waste_category) ~ "Plastic irrigation pipes",
    grepl("A17", waste_category) ~ "Fragments of non-foamed plastic (Hard plastic)",
    grepl("A18", waste_category) ~ "Plastic shotgun cartridges",
    grepl("A19", waste_category) ~ "Fragments of foamed plastic",
    grepl("A20", waste_category) ~ "Crisp packets/sweet wrappers",
    grepl("A21", waste_category) ~ "Plastic stickers"
  ))
```


## Design
### Theme publish
Layout maken voor de figuren, je kan in je figuren dan theme aanpassen naar theme_publish en dan zien al jouw figuren er hetzelfde uit. Je kan hieruit de layout aanpassen en dan je script lopen en dan veranderen al je figuren in 1 keer. Aanpassingen 
```{r include=TRUE}
theme_publish <- function () {
  theme(
    # add axis lines
    axis.line.y = element_line(color = "darkgrey"),
    axis.line.x = element_line(color = "darkgrey"),
    # remove the background
    panel.background = element_blank(), 
    # the gridlines of the y-axis 
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.2), 
    panel.grid.minor.y = element_line(colour = "lightgrey", linewidth = 0.2), 
    # the gridlines of the x-axis
    panel.grid.major.x = element_line(colour = "lightgrey", linewidth = 0.2), 
    panel.grid.minor.x = element_line(colour = "lightgrey", linewidth = 0.2), 
    # size of the titles
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 14),
    plot.title = element_text(hjust = 0, size = 16, face = "bold"),
    #axis.text.x = element_blank(),
    #remove background legend
    legend.key = element_blank()
    )
}

```


### Colour scheme

#### Colour macromaterial category
##### A - Plastic 
```{r}
order_plastic_category <- c(paste0("A", 1:21))

# Create a colour code with HEX colours
fcol_plastic_type <- c("#e8908b", "#df6f6a", "#d96a65", "#d36560", "#cc605b", 
                           "#c55a56", "#be5551", "#b74f4c", "#b04947", "#a94342", 
                           "#a23d3d", "#9b3738", "#942f33", "#8d272e", "#861f29", 
                           "#7f1724", "#780e1f", "#710618", "#6a000f", "#630006", 
                           "#5c0000")

# Name the colours
names(fcol_plastic_type) <- order_plastic_category

# Visualize the colours for each plastic category
plot(
  factor(order_plastic_category, order_plastic_category), 
  col = fcol_plastic_type
  )
```

##### B - Metal
```{r}
order_metal_category <- c(paste0("B", 1:8))

# Create a colour code with HEX colours
fcol_metal_type <- c("#f2e5c2", "#f0cd6e", "#edbb2f","#fcbf17", "#e39b49", "#de8716", "#bf720d", "#a35e03")

# Name the colours
names(fcol_metal_type) <- order_metal_category

# Visualize the colours for each metal category
plot(
  factor(order_metal_category, order_metal_category), 
  col = fcol_metal_type
  )
```

##### C - Rubber
```{r}
order_rubber_category <- c(paste0("C", 1:5))

# Create a colour code with HEX colours
fcol_rubber_type <- c("#f0e878", "#e6db4c", "#c9be1c", "#d9c004", "#c99402")

# Name the colours
names(fcol_rubber_type) <- order_rubber_category

# Visualize the colours for each plastic category
plot(
  factor(order_rubber_category, order_rubber_category), 
  col = fcol_rubber_type
  )
```

##### D - Glass
```{r}
order_glass_category <- c(paste0("D", 1:4))

# Create a colour code with HEX colours
fcol_glass_type <- c("#a6f5e5", "#5cd1ba", "#279c84", "#036e58")

# Name the colours
names(fcol_glass_type) <- order_glass_category

# Visualize the colours for each plastic category
plot(
  factor(order_glass_category, order_glass_category), 
  col = fcol_glass_type
  )
```

##### E - Natural products
```{r}
order_natural_category <- c(paste0("E", 1:5))

# Create a colour code with HEX colours
fcol_natural_type <- c("#9fe0b1", "#34e062", "#0e8c30", "#086320", "#023b11")

# Name the colours
names(fcol_natural_type) <- order_natural_category

# Visualize the colours for each plastic category
plot(
  factor(order_natural_category, order_natural_category), 
  col = fcol_natural_type
  )
```


##### F - Miscellaneaus
```{r}
order_Mis_category <- c(paste0("F", 1:3))

# Create a colour code with HEX colours
fcol_Mis_type <- c("#C6DBEF", "#6BAED6", "#084594")

# Name the colours
names(fcol_Mis_type) <- order_Mis_category

# Visualize the colours for each plastic category
plot(
  factor(order_Mis_category, order_Mis_category), 
  col = fcol_Mis_type
  )
```

##### G - Ceramics
```{r}
order_ceramics_category <- c(paste0("G", 1:6))

# Create a colour code with HEX colours
fcol_ceramics_type <- c("#e9d7fa", "#bd96e0", "#c395ed", "#aa50d4", "#a151ed", "#7f14e3", "#4d0491")

# Name the colours
names(fcol_ceramics_type) <- order_ceramics_category

# Visualize the colours for each plastic category
plot(
  factor(order_ceramics_category, order_ceramics_category), 
  col = fcol_ceramics_type
  )
```

# MACROLITTER
## DATA EXPLORATION 
### Summary
Summary of the mean, amount of fields, SD, SE and CI grouped by country.
```{r}
# Specify the columns you want to summarize
cols_to_summarize <- names(MACRO_all)[100:109]  # Replace with your actual column names

# Create long-format summary table
summary_table <- MACRO_all %>%
  summarize(across(all_of(cols_to_summarize), list(
    Mean = ~mean(.x, na.rm = TRUE),
    Median =~median(.x, na.rm = TRUE),
    SD   = ~sd(.x, na.rm = TRUE),
    SE   = ~sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x))),
    Min  = ~min(.x, na.rm = TRUE),
    Max  = ~max(.x, na.rm = TRUE),
    CI.lower = ~mean(.x, na.rm = TRUE) - 2 * sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x))),
    CI.upper = ~mean(.x, na.rm = TRUE) + 2 * sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))
  ), .names = "{.col}_{.fn}")) %>%
  pivot_longer(
    everything(),
    names_to = c("Variable", "Statistic"),
    names_sep = "_(?=[^_]+$)",  # <- split on last underscore only
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = Statistic,
    values_from = Value)

summary_table
```
```{r}
columns_to_summarize <- c("Total_onlymacro_material", "Total_onlymacro_plastic", "Total_onlymacro_metals", "Total_onlymacro_rubber", "Total_onlymacro_glass", "Total_onlymacro_mis", "Total_onlymacro_NaturP", "Total_onlymacro_Ceramics", "A2", "A17", "A21", "A20", "A3", "A13", "A14","A6", "A5", "A19")

summary <- data.frame(
  Variable = columns_to_summarize,
  Mean = sapply(MACRO_all[ , columns_to_summarize], function(x) mean(x, na.rm = TRUE)),
  SD = sapply(MACRO_all[ , columns_to_summarize], function(x) sd(x, na.rm = TRUE)),
  SE = sapply(MACRO_all[ , columns_to_summarize], function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x)))),
  Min  = sapply(MACRO_all[, columns_to_summarize], function(x) min(x, na.rm = TRUE)),
  Max  = sapply(MACRO_all[, columns_to_summarize], function(x) max(x, na.rm = TRUE))
)


MACRO_all %>%
  summarise(across(all_of(columns_to_summarize), ~ sum(.x, na.rm = TRUE)))


summary
```
Volgorde macro-sized litter: A2 - A17 - A20 - A13 - A3 - A14 - A6 - A21 - A19



## DATA VISUALISATION
### Staafdiagrammen of all categories
```{r}
# Define the sub-categories. As R will place automatically 1,10 next to each other, the categories would switch from place.
ordered_levels <- c(paste0("A", 1:21),
                    paste0("B", 1:8),
                    paste0("C", 1:5),
                    paste0("D", 1:4),
                    paste0("E", 1:5),
                    paste0("F", 1:3),
                    paste0("G", 1:6))

# Maak een factor aan met de gewenste niveaus
MAP_mean_categories_macro$Subcategories <- factor(MAP_mean_categories_macro$Subcategories, levels = ordered_levels)
```

**Plastic**

```{r}
Staaf_plastic_macro <- ggplot(MAP_mean_categories_macro[1:21, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_plastic_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  
  theme_publish() +
  ylab("Mean number of macroplastics/Ha")  +
  xlab("Plastic subcategories")

Staaf_plastic_macro
#ggsave("Plots_macro/Staaf_plastic_macro.pdf", width = 15, height = 5, dpi = 600)
```
**Metal**
```{r}
Staaf_metal_macro <- ggplot(MAP_mean_categories_macro[22:29, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_metal_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  theme_publish() +
  ylab("Mean number of macrometal/Ha")  +
  xlab("Metal subcategories")

Staaf_metal_macro
#ggsave("Plots_macro/Staaf_plastic_macro.pdf", width = 15, height = 5, dpi = 600)
```

**Rubber**

```{r}
Staaf_rubber_macro <- ggplot(MAP_mean_categories_macro[30:34, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_rubber_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  theme_publish() +
  ylab("Mean number of macrorubber/Ha")  +
  xlab("Rubber subcategories")

Staaf_rubber_macro
#ggsave("Plots_macro/Staaf_plastic.pdf", width = 15, height = 5, dpi = 600)
```

**Glass**
```{r}
Staaf_glass_macro <- ggplot(MAP_mean_categories_macro[35:38, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_glass_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  theme_publish() +
  ylab("Mean number of macro glass/Ha")  +
  xlab("Glass subcategories")

Staaf_glass_macro
#ggsave("Plots_macro/Staaf_plastic.pdf", width = 15, height = 5, dpi = 600)
```

**Natural products**
```{r}
Staaf_NP_macro <- ggplot(MAP_mean_categories_macro[39:43, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_natural_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  theme_publish() +
  ylab("Mean number of macro natural products/Ha")  +
  xlab("Natural products subcategories")

Staaf_NP_macro
#ggsave("Plots_macro/Staaf_plastic.pdf", width = 15, height = 5, dpi = 600)
```


**Miscellaneous**
```{r}
Staaf_mis_macro <- ggplot(MAP_mean_categories_macro[44:46, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_Mis_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  theme_publish() +
  ylab("Mean number of macro miscellaneous/Ha")  +
  xlab("Miscellaneous Subcategories")

Staaf_mis_macro
#ggsave("Plots_macro/Staaf_plastic.pdf", width = 15, height = 5, dpi = 600)
```

**Ceramics**
```{r}
Staaf_ceramics_macro <- ggplot(MAP_mean_categories_macro[47:52, ], aes(x = Subcategories, y = Mean_macro, fill = Subcategories)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =  fcol_ceramics_type, name = "Subcategories") +
  geom_errorbar(aes(ymin = Mean_macro - SE, ymax = Mean_macro + SE), width = 0.2) +
  
  theme_publish() +
  ylab("Mean number of macro ceramics/Ha")  +
  xlab("Ceramics Subcategories")

Staaf_ceramics_macro
#ggsave("Plots_macro/Staaf_plastic.pdf", width = 15, height = 5, dpi = 600)
```
```{r}
Plot_staaf_macro <- Staaf_plastic_macro / (Staaf_metal_macro+Staaf_rubber_macro)/(Staaf_glass_macro + Staaf_NP_macro)/(Staaf_mis_macro + Staaf_ceramics_macro) +
    plot_annotation(tag_levels = "A") &
  theme(plot.margin = margin(10, 20, 10, 20))
#Plot_staaf_macro_woMC240
ggsave("Plots_macro/Plot_staaf_macro_woOutliers.png", width = 15, height = 18, dpi = 600)

```

### Histograms of all categories
#### Counts
Calculation of mean and median of Total_onlymacro_plastics

```{r}
mean_total_litter <- mean(MACRO$Total_onlymacro_material)
median_total_litter <- median(MACRO$Total_onlymacro_material)
```
**Histogram of Total_macromaterials:**

```{r}
Plot_histcounts_macro <- ggplot(MACRO) +
  geom_histogram(aes(Total_onlymacro_material), bins = 30, alpha = 0.7) +
  #scale_x_continuous(limits = c(0, 3000)) +
  geom_vline(aes(xintercept = mean_total_litter), linetype = "dashed", size = 1, color = '#0736ad') +
  annotate("text", x = mean_total_litter + 60000, y = 70, label = paste("Mean =", round(mean_total_litter, 2)), size = 5, color = '#0736ad') +
  geom_vline(aes(xintercept = median_total_litter), linetype = "dashed", size = 1, color = '#07a5ad') +
  annotate("text", x = median_total_litter + 60000, y = 50, label = paste("Median =", round(median_total_litter, 2)), size = 5, color = '#07a5ad') +
  ylab("Count") +
  xlab("Total macrolitter count") +
  labs( tag = "A") +
  theme_publish()

Plot_histcounts_macro

```
Histogram is skewed to the left, so we will try to log10 transform the data.

#### Log counts
In this step, we are going to use log-transformed data to create histograms. We will use log10 transformation

```{r}
mean_log_total_litter <- mean(MACRO_all$log_Total_macrolitter)
median_log_total_litter <- median(MACRO_all$log_Total_macrolitter)
```

##### Histogram of Total_macromaterials log transformed:

```{r}
Plot_histlogcounts_macro <- ggplot(MACRO_all) +
  geom_histogram(aes(log_Total_macrolitter), binwidth = 0.1) +
  geom_vline(aes(xintercept = mean_log_total_litter), linetype = "dashed", size = 1, color = '#0736ad') +
  annotate("text", x = mean_log_total_litter + 2, y = 25, label = paste("Mean =", round(mean_log_total_litter, 2)), size = 5, color = '#0736ad') +
  geom_vline(aes(xintercept = median_log_total_litter), linetype = "dashed", size = 1, color = '#07a5ad') +
  annotate("text", x = median_log_total_litter + 2, y = 20, label = paste("Median =", round(median_log_total_litter, 2)), size = 5, color = '#07a5ad') +
  ylab("Frequency") +
  xlab("Log10 of total macrolitter count/Ha") +
  theme_publish()

Plot_histlogcounts_macro
```
The histogram is a little skewed to the left. The difference between mean and median is minor.

**Plastic**
```{r}
Hist_macroplastic <- ggplot(MACRO_all, aes(x = log_Total_macroplastic)) +
  geom_histogram(bins = 30, fill = "#cc605b", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macroplastic)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macroplastic) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macroplastic), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macroplastic)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macroplastic) + 1, y = 28, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macroplastic), 2)), size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total plastic/Ha", y = "Frequency")

Hist_macroplastic

```

**Metal**
```{r}
Hist_macrometal <- ggplot(MACRO_all, aes(x = log_Total_macrometal)) +
  geom_histogram(bins = 30, fill = "#e39b49", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macrometal)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macrometal) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macrometal), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macrometal)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macrometal) + 1, y = 50, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macrometal), 2)), size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total metal/Ha", y = "Frequency")

Hist_macrometal

```
**Rubber**
```{r}
Hist_macrorubber <- ggplot(MACRO_all, aes(x = log_Total_macrorubber)) +
  geom_histogram(bins = 30, fill = "#e6db4c", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macrorubber)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macrorubber) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macrorubber), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macrorubber)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macrorubber) + 1, y = 40, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macrorubber), 2)), size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total rubber/Ha", y = "Frequency")

Hist_macrorubber

```

**Glass**
```{r}
Hist_macroglass <- ggplot(MACRO_all, aes(x = log_Total_macroglass)) +
  geom_histogram(bins = 30, fill = "#5cd1ba", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macroglass)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macroglass) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macroglass), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macroglass)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macroglass) + 1, y = 40, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macroglass), 2)), size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total glass/Ha", y = "Frequency")

Hist_macroglass

```
**Natural products**
```{r}
Hist_macroNP <- ggplot(MACRO_all, aes(x = log_Total_macroNP)) +
  geom_histogram(bins = 30, fill = "#0e8c30", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macroNP)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macroNaturP) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macroNP), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macroNP)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macroNP) + 1, y = 45, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macroNP), 2)), size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total natural products/Ha", y = "Frequency")

Hist_macroNP

```

**Miscellaneous**
```{r}
Hist_macromis <- ggplot(MACRO_all, aes(x = log_Total_macromis)) +
  geom_histogram(bins = 30, fill = "#6BAED6", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macromis)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macromis) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macromis), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macromis)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macromis) + 1, y = 45, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macromis), 2)), size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total miscellaneous/Ha", y = "Frequency")

Hist_macromis

```


**Ceramics**
```{r}
Hist_macroceramics <- ggplot(MACRO_all, aes(x = log_Total_macroceramics)) +
  geom_histogram(bins = 30, fill = "#7f14e3", alpha = 0.8) +
  
  # Mean
  geom_vline(aes(xintercept = mean(log_Total_macroceramics)), 
             linetype = "dashed", size = 1) +
  
  annotate("text", x = mean(MACRO_all$log_Total_macroceramics) + 1, y = 25, 
           label = paste("Mean =", round(mean(MACRO_all$log_Total_macroceramics), 2)), size = 5) +
  
  # Median
  geom_vline(aes(xintercept = median(log_Total_macroceramics)), linetype = "dashed", size = 1, color = '#7a7878') +
  
  annotate("text", x = median(MACRO_all$log_Total_macroceramics) + 1, y = 30, 
           label = paste("Median =", round(median(MACRO_all$log_Total_macroceramics), 2)), 
           size = 5, color = '#7a7878') +
  
  theme_publish() +
  labs(x = "Log10 of total ceramics/Ha", y = "Frequency")

Hist_macroceramics

```


```{r}
Hist_categories_macro <- (Plot_histlogcounts_macro+Hist_macroplastic) / (Hist_macrometal+Hist_macrorubber)/(Hist_macroglass + Hist_macroNP)/(Hist_macromis + Hist_macroceramics) +
    plot_annotation(tag_levels = "A") &
  theme(plot.margin = margin(10, 20, 10, 20))
Hist_categories_macro
ggsave("Plots_macro/Hist_macrocategories.png", width = 10, height = 15, dpi = 600)
```

# MACROPLASTIC
## DATA EXPLORATION

### Summary
Summary of the mean, amount of fields, SD, SE and CI grouped by country.
```{r}
summary <- MACRO %>%
  group_by(Country) %>% #onderverdelen in groepen, je kan hier ook meerder aan meegeven zoals bv compost
  dplyr::summarize(Mean = mean(Total_onlymacro_plastic, na.rm = TRUE),
             n = n(),
             SD = sd(Total_onlymacro_plastic,na.rm = TRUE),
             SE = sd(Total_onlymacro_plastic, na.rm = TRUE)/sqrt(n),
             CI.lower = Mean - 2*SE,
             CI.upper = Mean + 2*SE) #%>%
  #formattable
 
summary
```

## DATA VISUALISATION
### Boxplot TO DO BOXPLOT BODEMTEXTUUR
**Boxplot - Country**
```{r}
Boxplot_country_macro <- ggplot(MACRO_all, aes(x = Country, y = Total_onlymacro_plastic)) +
  geom_boxplot(outlier.shape = 2) +
  geom_jitter() +
  theme_publish() + 
  
  labs(title = "Total Number of Plastics by Country",
       x = "Country", y = "Total Number of Plastics") 
Boxplot_country_macro
```

## CORRELATION
### Veld bewerkingen
Enkele velden zijn hier niet in opgenomen aangezien ze geen gegevens over de bewerkingen van het veld bevatten.

```{r}
# Correlation matrix
# One hot encoding for numerical variables
MACRO_all_noNA <- MACRO_all_noNA %>%
  mutate(
    Compost_binary = ifelse(Compost == "Yes", 1, 0),
    Manure_binary = ifelse(Manure == "Yes", 1, 0),
    Pesticides_binary = ifelse(pesticides == "Yes", 1, 0),
    Crop_rotation_binary = ifelse(crop_rotation == "Yes", 1, 0),
    Irrigation_yesno_binary = ifelse(Irrigationyesno == "Yes", 1, 0)
      ) %>%
  dummy_cols(select_columns = c("tillage", "Irrigation", "Usage_plastic_foil"), remove_selected_columns = FALSE)

# Variables for our research question with one hot enconding
correlation_data <- MACRO_all_noNA %>%
  dplyr::select(
    log_Total_macroplastic, 
    Compost_binary, 
    Manure_binary, 
    Pesticides_binary,
    Crop_rotation_binary,
    starts_with("tillage_"),
    starts_with("Irrigation_"),
    starts_with("Usage_plastic_foil_")
  )  
str(correlation_data)
# Compute correlation matrix
cor_matrix <- cor(correlation_data, use = "complete.obs", method = "pearson")

# Plot Correlation matrix 

cor_macrodata <- melt(cor_matrix)
cor_macroheatmap <- ggplot(cor_macrodata, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1, 1)) +
  labs(title = "Correlation Matrix",
       x = "Variables",
       y = "Variables",
       fill = "Correlation Coefficient")+  
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
cor_macrodata
print(cor_macroheatmap)
#ggsave("cor_heatmap_bewerkingen_macro.pdf", width = 10, height = 10)
```

### Soil index & Location index
```{r}
correlation_macrodata <- MACRO_all %>%
  dplyr::select(
    log_Total_macroplastic, 
    soilindex,
    location_index,
    total_index)

# Compute correlation matrix
cor_macromatrix <- cor(correlation_data, use = "complete.obs", method = "pearson")

# Plot Correlation matrix 

cor_macrodata <- melt(cor_macromatrix)
cor_macroheatmap <- ggplot(cor_macrodata, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1, 1)) +
  labs(title = "Correlation Matrix",
       x = "Variables",
       y = "Variables",
       fill = "Correlation Coefficient")+  
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
print(cor_macroheatmap)
ggsave("cor_heatmap_macroindex.pdf", plot = cor_macroheatmap, width = 10, height = 10)
```
All indexes are positively correlated with log_Total_onlymacro_plastic

### Distance only for Belgium!
```{r}
correlation_data <- MACRO_Belgium %>%
  dplyr::select(
    log_Total_macroplastic, 
    distance_city,
    distance_highway,
    distance_industrie_VL,
    distance_industrie_WL,
    distance_recypark_VL,
    distance_village,
    distance_recypark_WL,
    distance_waste_industriel_WL,
    Distance_primroutes,
    min_distance_waste,
    min_distance_industry)

# Compute correlation matrix
cor_matrix <- cor(correlation_data, use = "complete.obs", method = "pearson")

# Plot Correlation matrix 

cor_data <- melt(cor_matrix)
cor_heatmap <- ggplot(cor_data, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1, 1)) +
  labs(title = "Correlation Matrix",
       x = "Variables",
       y = "Variables",
       fill = "Correlation Coefficient")+  
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
cor_data
print(cor_heatmap)
ggsave("cor_heatmap_macro_distance.pdf", plot = cor_heatmap, width = 10, height = 10)
```
Positive correlations between Log_Total_onlymacro_plastics and the distances:

- Distance_city: 0.079579668
- Distance_industry_Vl: 0.074441577
- distance_industrie_WL: 0.019467392
- distance_recypark_VL: 0.074881194	
- distance_village: 0.082748693	
- distance_recypark_WL: 0.016467461
- distance_waste_industriel_WL: 0.008893326	
- Distance_primroutes: 0.038875558
- min_distance_waste: 0.106322994
- min_distance_industry: 0.125237310	

Negative correlations between Log_Total_onlymacro_plastic and the distances of Belgium:

- Distance_highway: -0.036360331

# Pie chart field management
Here will be worked with the dataset without MC24_240 

```{r}
# Convert to factors (optional, for clean labeling)
Compost <- factor(MACRO_all_noNA_wo$Compost, levels = c("Yes", "No"))
Manure <- factor(MACRO_all_noNA_wo$Manure, levels = c("Yes", "No"))
Irrigation <- factor (MACRO_all_noNA_wo$Irrigation, levels = c("Other", "No", "Groundwater", "Surface_water", "Treated_wastewater", "Drinking_water"))
Plastic_usage <- factor (MACRO_all_noNA_wo$Usage_plastic_foil, levels = c("Yes_Bioplastics", "Yes_other_plastics", "No"))
Tillage <- factor (MACRO_all_noNA_wo$tillage, levels = c("Ploughing", "Non_inverted_tillage", "No"))
Crop_rotation <- factor(MACRO_all_noNA_wo$crop_rotation, levels = c("Yes", "No"))
pesticides <- factor(MACRO_all_noNA_wo$pesticides, levels = c("Yes", "No"))
```

```{r}
# Function to prepare pie chart data
prepare_pie_data <- function(column_data, col_name) {
  df <- data.frame(Response = column_data) %>%
    mutate(Response = as.character(Response),
           Response = ifelse(is.na(Response), "NA", Response)) %>%
    group_by(Response) %>%
    summarise(Count = n()) %>%
    mutate(Column = col_name)
  return(df)
}

# Prepare data for both columns
data_Compost_1 <- prepare_pie_data(MACRO_all_noNA_wo$Compost, "Compost")
data_Manure <- prepare_pie_data(MACRO_all_noNA_wo$Manure, "Manure")
data_Usage_plastic <- prepare_pie_data(MACRO_all_noNA_wo$Usage_plastic_foil, "Usage_plastic_foil")
data_Usage_plasticyesno <- prepare_pie_data(MACRO_all_noNA_wo$Plasticyesno, "Usage_plastic_foil_yesno")
data_tillage <- prepare_pie_data(MACRO_all_noNA_wo$tillage, "Tillage")
data_pesticides <- prepare_pie_data(MACRO_all_noNA_wo$pesticides, "pesticides")
data_croprotation <- prepare_pie_data(MACRO_all_noNA_wo$crop_rotation, "Crop_rotation")
data_irrigation <- prepare_pie_data(MACRO_all_noNA_wo$Irrigation, "Irrigation")
data_irrigation_yesno <- prepare_pie_data(MACRO_all_noNA_wo$Irrigationyesno, "Irrigation_yesno")
```


```{r}
# Plot with ggplot2
Compost_pie <- ggplot(data_Compost_1, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  labs(title = "Compost", x = NULL, y = NULL) +
  theme_void()
Compost_pie
```
Total = 197
```{r}
Manure_pie <- ggplot(data_Manure, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Manure", x = NULL, y = NULL) +
  theme_void() 
Manure_pie
```

 Total = 197
```{r}
Irrigation_pie <- ggplot(data_irrigation, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Irrigation", x = NULL, y = NULL) +
  theme_void()

Irrigation_pie
```

```{r}
Plastic_pie <- ggplot(data_Usage_plastic, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Usage of plastic foil", x = NULL, y = NULL) +
  theme_void()
Plastic_pie
```

```{r}
Plastic_pie_yesno <- ggplot(data_Usage_plasticyesno, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Usage of plastic foil", x = NULL, y = NULL) +
  theme_void()
Plastic_pie_yesno
```

```{r}
Pesticides_pie <- ggplot(data_pesticides, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Pesticides", x = NULL, y = NULL) +
  theme_void()
Pesticides_pie 
```

```{r}
Tillage_pie <- ggplot(data_tillage, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Tillage", x = NULL, y = NULL) +
  theme_void()
Tillage_pie
```

```{r}
croprotation_pie <- ggplot(data_croprotation, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = Count), color = "white", size = 4, position = position_stack(vjust = 0.5)) +
  labs(title = "Crop rotation", x = NULL, y = NULL) +
  theme_void()
croprotation_pie
```

```{r}
Irrigation_yesno_pie <- ggplot(data_irrigation_yesno, aes(x = "", y = Count, fill = Response)) +
  geom_bar(stat = "identity", width = 1) +
  geom_text(aes(label = Count), 
            color = "white", 
            size = 4,
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  labs(title = "Irrigation_yesno", x = NULL, y = NULL) +
  theme_void()
Irrigation_yesno_pie
```
Total = 197

```{r}
plot_pie <- ((Manure_pie + Compost_pie + Irrigation_yesno_pie) / (Pesticides_pie + croprotation_pie + Plastic_pie_yesno) + (Tillage_pie + plot_layout(guides = 'keep'))) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
plot_pie

ggsave("plot_pie_woMC240.png", width = 10, height = 12, dpi = 600)
```

# Negative binomiaal model field management
To do a NB model, you need to have count data (integers). Our data are not real counts anymore as they are transformed to counts/hectare.

You can do this within the model by taking the count data and adding the area in an offset. I tried it with the surface_Ha but some field are to small to use. Log(0.0004) is negative and could not be used in the model. Therefore, I tried using surface_m2. This is the model below. We see that is not a good fit as the overdispersion is 9.6788
```{r}
model_NB1 <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ (Compost + Manure + pesticides + Irrigationyesno + Plasticyesno + tillage)^2,
  offset(log(Surface_m2)), 
  data = MAP_all_noNA, 
  control = glm.control(maxit = 100)
  )

summary(model_NB1)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB1)
```
With the two-way interactions, the compost:tillagePlouging gives NA, due to multicollinearity (checked with alias)
```{r}
model_NB <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ (Compost + Manure + pesticides + Irrigationyesno + Plasticyesno)^2 + tillage + tillage:Manure + tillage:pesticides + tillage:Irrigationyesno + tillage:Plasticyesno,
  offset(log(Surface_m2)), 
  data = MAP_all_noNA, 
  control = glm.control(maxit = 100)
  )

summary(model_NB)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB)
```
Compost, Manure, Pesticides, irrigation and plastic usage have a p-value < 0.05. 
ManureYes:PlasticyesnoYes
pesticidesYes:PlasticyesnoYes
IrrigationyesnoYes:PlasticyesnoYes
ManureYes:tillageNon_inverted_tillage
ManureYes:tillagePloughing
pesticidesYes:tillageNon_inverted_tillage
pesticidesYes:tillagePloughing
IrrigationyesnoYes:tillageNon_inverted_tillage
IrrigationyesnoYes:tillagePloughing
PlasticyesnoYes:tillageNon_inverted_tillage
PlasticyesnoYes:tillagePloughing

We see an effect of the use of plastic and tillage within interaction with the other field management parameters. 

```{r}
#overdispersion check
overdispersion <- deviance(model_NB) / df.residual(model_NB)
print(overdispersion)

#multicollinearity: see if the predictors are highly correlated
vif(model_NB, type = 'terms')  

#Used to see if you model is better than another model
AIC(model_NB)

#Shira said to use stepAIC to find the best model
best_model <- stepAIC(model_NB, direction = "both", trace = FALSE)
summary(best_model)
```
## ANOVA field management

```{r}
anova <- anova(model_NB, test = "Chisq")

anova
```
```{r}
confint(model_NB)
```


## Boxplots field management - Effect of tillage 
Does ploughing or non-inverted tillage enhance the effect of possible sources of plastic?

Tillage consist out of 6 samples with the answer no ==> we will filter those out to make the boxplots
```{r}
tillage_filtered <- MAP_all_noNA %>% 
  filter(tillage %in% c("Non_inverted_tillage", "Ploughing"))

#  levels = c("Non_inverted_tillage", "Ploughing"),
#  labels = c("Non-inverted tillage", "Ploughing")
#)
```
### Compost

```{r}
em_til_compost <- emmeans(model_NB, pairwise ~ tillage * Compost, adjust = "tukey")
em_til_compost

cld_til_compost <- cld(em_til_compost, Letters = letters, adjust = "tukey")

cld_subset_compost <- cld_til_compost %>%
  filter(tillage %in% c("Ploughing", "Non_inverted_tillage"))

cld_subset_compost

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(tillage_filtered$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot
Boxplot_Compost_tillage <- ggplot(tillage_filtered, aes(x = Compost, y = log_Total_onlymacro_plastic, fill = tillage)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ tillage) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  #geom_text(data = cld_subset_compost, aes(x = Compost, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Compost usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_Compost_tillage
```

### Manure
```{r}
em_til_man <- emmeans(model_NB, pairwise ~ tillage * Manure, adjust = "tukey")
em_til_man

cld_til_man <- cld(em_til_man, Letters = letters, adjust = "tukey")

cld_subset_manure <- cld_til_man %>%
  filter(tillage %in% c("Ploughing", "Non_inverted_tillage"))

cld_subset_manure

Boxplot_Manure_tillage <- ggplot(tillage_filtered, aes(x = Manure, y = log_Total_onlymacro_plastic, fill = tillage)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  facet_wrap(~ tillage) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_subset_manure, aes(x = Manure, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Manure usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_Manure_tillage
```

### Pesticides
```{r}
em_til_pest <- emmeans(model_NB, pairwise ~ tillage * pesticides, adjust = "tukey")
em_til_pest

cld_em_pest <- cld(em_til_pest, Letters = letters, adjust = "tukey")
print(cld_em_pest)

cld_subset_pest <- cld_em_pest %>%
  filter(tillage %in% c("Ploughing", "Non_inverted_tillage"))

cld_subset_pest

Boxplot_pest_tillage <- ggplot(tillage_filtered, aes(x = pesticides, y = log_Total_onlymacro_plastic, fill = tillage)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  facet_wrap(~ tillage) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_subset_pest, aes(x = pesticides, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_pest_tillage
```
### Irrigation

```{r}
em_til_irr <- emmeans(model_NB, pairwise ~ tillage * Irrigationyesno, adjust = "tukey")
em_til_irr

cld_em_irr <- cld(em_til_irr, Letters = letters, adjust = "tukey")

cld_subset_irr <- cld_em_irr %>%
  filter(tillage %in% c("Ploughing", "Non_inverted_tillage"))

cld_subset_irr

Boxplot_irri_tillage <- ggplot(tillage_filtered, aes(x = Irrigationyesno, y = log_Total_onlymacro_plastic, fill = tillage)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  facet_wrap(~ tillage) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  #geom_text(data = cld_subset_irr, aes(x = Irrigationyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() +
  
  labs(title = "",
       x = "Irrigation", y = "Log10 Plastic counts/Hectare") 
Boxplot_irri_tillage
```

Both the interaction between irrigation and non-intverted tillage and ploughing is significant. 

### Plastic usage
```{r}
em_til_plastic <- emmeans(model_NB, pairwise ~ tillage * Plasticyesno, adjust = "tukey")

em_til_plastic

cld_em_plastic <- cld(em_til_plastic, Letters = letters, adjust = "tukey")
print(cld_em_plastic)

cld_subset_plastic <- cld_em_plastic %>%
  filter(tillage %in% c("Ploughing", "Non_inverted_tillage"))

cld_subset_plastic

Boxplot_plastic_tillage <- ggplot(tillage_filtered, aes(x = Plasticyesno, y = log_Total_onlymacro_plastic, fill = tillage)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ tillage) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  #geom_text(data = cld_subset_plastic, aes(x = Plasticyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() +
  
  labs(title = "",
       x = "Plastic foil usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_plastic_tillage
```
A significant difference could be measured between the interaction between NIT and plastic usage (p = 0.0004)
No significant difference could be measured between the interaction of ploughing and plastic usage.


```{r}
plot_boxplot <- ((Boxplot_Compost_tillage + Boxplot_Manure_tillage) / (Boxplot_pest_tillage + Boxplot_irri_tillage)/Boxplot_plastic_tillage) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_boxplot_fieldmanagement.png", width = 10, height = 12, dpi = 600)
ggsave("plot_boxplot_fieldmanagement.pdf", width = 10, height = 12, dpi = 600)
```


## Barplots field management - effect of tillage LOG

```{r}
summary_data_compost <- tillage_filtered %>%
  group_by(tillage, Compost) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_compost <- ggplot(summary_data_compost, aes(x = Compost, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_compost, aes(x = Compost, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_compost
```

```{r}
summary_data_manure <- tillage_filtered %>%
  group_by(tillage, Manure) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_manure <- ggplot(summary_data_manure, aes(x = Manure, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_manure, aes(x = Manure, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Manure Treatment") +
  theme_publish()
```

```{r}
summary_data_pest <- tillage_filtered %>%
  group_by(tillage, pesticides) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_pest <- ggplot(summary_data_pest, aes(x = pesticides, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_pest, aes(x = pesticides, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
```
```{r}
summary_data_irr <- tillage_filtered %>%
  group_by(tillage, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_irr <- ggplot(summary_data_irr, aes(x = Irrigationyesno, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_irr, aes(x = Irrigationyesno, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Usage of Irrigation") +
  theme_publish()
```
```{r}
summary_data_plastic <- tillage_filtered %>%
  group_by(tillage, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_plastic <- ggplot(summary_data_plastic, aes(x = Plasticyesno, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_plastic, aes(x = Plasticyesno, y = 3, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Usage of plastic") +
  theme_publish()

barplot_plastic
```
```{r}
plot_barplot <- ((barplot_compost + barplot_manure) / (barplot_pest + barplot_irr)/barplot_plastic) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_fieldmanagement.pdf", width = 10, height = 12, dpi = 600)
```

## Barplots field management - effect of tillage

### Compost

```{r}
summary_data_compost <- tillage_filtered %>%
  group_by(tillage, Compost) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_compost <- ggplot(summary_data_compost, aes(x = Compost, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  #geom_text(data = cld_subset_compost, aes(x = Compost, y = 7500, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_compost
```
### Manure
```{r}
summary_data_manure <- tillage_filtered %>%
  group_by(tillage, Manure) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_manure <- ggplot(summary_data_manure, aes(x = Manure, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_manure, aes(x = Manure, y = 1550, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_manure
```
### Pesticides

```{r}
summary_data_pest <- tillage_filtered %>%
  group_by(tillage, pesticides) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_pest <- ggplot(summary_data_pest, aes(x = pesticides, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_subset_pest, aes(x = pesticides, y = 1500, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_pest
```

### Irrigation
```{r}
summary_data_irr <- tillage_filtered %>%
  group_by(tillage, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_irr <- ggplot(summary_data_irr, aes(x = Irrigationyesno, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  #geom_text(data = cld_subset_irr, aes(x = Irrigationyesno, y = 15000, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Usage of Irrigation") +
  theme_publish()
barplot_irr
```

### Plastic usage
```{r}
summary_data_plastic <- tillage_filtered %>%
  group_by(tillage, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_plastic <- ggplot(summary_data_plastic, aes(x = Plasticyesno, y = mean_plastic, fill = tillage)) +
  facet_wrap(~ tillage) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  #geom_text(data = cld_subset_plastic, aes(x = Plasticyesno, y = 3000, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Usage of plastic") +
  theme_publish()

barplot_plastic
```


```{r}
plot_barplot <- ((barplot_compost + barplot_manure) / (barplot_pest + barplot_irr)/barplot_plastic) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_fieldmanagement_withoutlog.pdf", width = 10, height = 12, dpi = 600)
```


# Plastic usage with pesticides
## Boxplot
```{r}
# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y_plastic <- max(MAP_all_noNA$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1
```


```{r}
em_plastic_pest <- emmeans(model_NB, pairwise ~ Plasticyesno * pesticides, adjust = "sidak")
em_plastic_pest

cld_em_pestplastic <- cld(em_plastic_pest, Letters = letters, adjust = "sidak")
print(cld_em_pestplastic)

Boxplot_pest_plastic <- ggplot(MAP_all_noNA, aes(x = pesticides, y = log_Total_onlymacro_plastic, fill = Plasticyesno)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  facet_wrap(~ Plasticyesno,
             labeller = labeller(Plasticyesno = c("Yes" = "Plastic usage", 
                                                "No" = "No Plastic usage"))) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_pestplastic, aes(x = pesticides, y = fixed_y_plastic, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_pest_plastic
```

# Field management België VS Nederland.
## Filter dataset België en Nederland

```{r}
MAP_BenN <- MAP_all_noNA %>%
  filter(Country %in% c("Belgium", "The Netherlands"))

```


## NB model with country
with the interaction with tillage
```{r}
model_NB_country <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ (Compost + Manure + pesticides + Irrigationyesno + Plasticyesno + Country)^2 + tillage + tillage:Manure + tillage:pesticides + tillage:Irrigationyesno + tillage:Plasticyesno,
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100)
  )

summary(model_NB_country)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country)
```

```{r}
#Shira said to use stepAIC to find the best model
best_model <- stepAIC(model_NB_country, direction = "both", trace = FALSE)
summary(best_model)
```

```{r}
model_NB_country_1 <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ Compost + Manure + pesticides + 
    Irrigationyesno + Plasticyesno + Country + tillage + Compost:Irrigationyesno + 
    Compost:Plasticyesno + Compost:Country + Manure:Plasticyesno + 
    Manure:Country + pesticides:Plasticyesno + pesticides:Country + 
    Irrigationyesno:Plasticyesno + Irrigationyesno:Country + 
    Manure:tillage + pesticides:tillage + Irrigationyesno:tillage + 
    Plasticyesno:tillage + Manure:pesticides, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_country_1)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country_1)
```

```{r}

anova <- anova(model_NB_country_1, test = "Chisq")

anova

```
## Country x Compost

```{r}
model_NB_country_compost <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ Compost * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_country_compost)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country_compost)
```

```{r}
em_compost_country <- emmeans(model_NB_country_compost, pairwise ~ Compost * Country, adjust = "sidak")
em_compost_country

cld_em_compost_country <- cld(em_compost_country, Letters = letters, adjust = "sidak")
print(cld_em_compost_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot

Boxplot_compost_country <- ggplot(MAP_BenN, aes(x = Compost, y = log_Total_onlymacro_plastic, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_compost_country, aes(x = Compost, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Compost usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_compost_country
```
**Barplot - Log**
```{r}
summary_data_compost <- MAP_BenN %>%
  group_by(Country, Compost) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_compost_BenN <- ggplot(summary_data_compost, aes(x = Compost, y = mean_plastic)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_compost_country, aes(x = Compost, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_compost_BenN
```
**Barplot**
```{r}
summary_data_compost <- MAP_BenN %>%
  group_by(Country, Compost) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_compost_BenN <- ggplot(summary_data_compost, aes(x = Compost, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_compost_country, aes(x = Compost, y = 2000, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_compost_BenN
```
## Country x Manure
```{r}
model_NB_country_manure <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ Manure * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_country_manure)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country_manure)
```
```{r}
em_manure_country <- emmeans(model_NB_country_manure, pairwise ~ Manure * Country, adjust = "sidak")
em_manure_country

cld_em_manure_country <- cld(em_manure_country, Letters = letters, adjust = "sidak")
print(cld_em_manure_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot

Boxplot_manure_country <- ggplot(MAP_BenN, aes(x = Manure, y = log_Total_onlymacro_plastic, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_manure_country, aes(x = Manure, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Manure usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_manure_country
```
**Barplot - Log**
```{r}
summary_data_Manure <- MAP_BenN %>%
  group_by(Country, Manure) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_Manure_BenN <- ggplot(summary_data_Manure, aes(x = Manure, y = mean_plastic)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_manure_country, aes(x = Manure, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_Manure_BenN
```


**Barplot**

```{r}
summary_data_Manure <- MAP_BenN %>%
  group_by(Country, Manure) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_Manure_BenN <- ggplot(summary_data_Manure, aes(x = Manure, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_manure_country, aes(x = Manure, y = 2000, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_Manure_BenN
```

## Country x Irrigation
```{r}
model_NB_country_irri <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ Irrigationyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_country_irri)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country_irri)
```

```{r}
em_irri_country <- emmeans(model_NB_country_irri, pairwise ~ Irrigationyesno * Country, adjust = "sidak")
em_irri_country

cld_em_irri_country <- cld(em_irri_country, Letters = letters, adjust = "sidak")
print(cld_em_irri_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot

Boxplot_irri_country <- ggplot(MAP_BenN, aes(x = Irrigationyesno, y = log_Total_onlymacro_plastic, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_irri_country, aes(x = Irrigationyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Irrigation usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_irri_country
```
**Barplot - Log**

```{r}
summary_data_irri <- MAP_BenN %>%
  group_by(Country, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_Irri_BenN <- ggplot(summary_data_irri, aes(x = Irrigationyesno, y = mean_plastic)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_irri_country, aes(x = Irrigationyesno, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Irrigation Treatment") +
  theme_publish()
barplot_Irri_BenN
```
**Barplot**
```{r}
summary_data_irri <- MAP_BenN %>%
  group_by(Country, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_Irri_BenN <- ggplot(summary_data_irri, aes(x = Irrigationyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_irri_country, aes(x = Irrigationyesno, y = 1500, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Irrigation Treatment") +
  theme_publish()
barplot_Irri_BenN
```

## Country x Pesticides
```{r}
model_NB_country_pest <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ pesticides * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_country_pest)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country_pest)
```

```{r}
em_pest_country <- emmeans(model_NB_country_pest, pairwise ~ pesticides * Country, adjust = "sidak")
em_pest_country

cld_em_pest_country <- cld(em_pest_country, Letters = letters, adjust = "sidak")
print(cld_em_pest_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot

Boxplot_pest_country <- ggplot(MAP_BenN, aes(x = pesticides, y = log_Total_onlymacro_plastic, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_pest_country, aes(x = pesticides, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_pest_country
```
**Barplot - Log**

```{r}
summary_data_Pest <- MAP_BenN %>%
  group_by(Country, pesticides) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_Pest_BenN <- ggplot(summary_data_Pest, aes(x = pesticides, y = mean_plastic)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_pest_country, aes(x = pesticides, y = 2.7, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_Pest_BenN
```
**Barplot**
```{r}
summary_data_Pest <- MAP_BenN %>%
  group_by(Country, pesticides) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_Pest_BenN <- ggplot(summary_data_Pest, aes(x = pesticides, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_pest_country, aes(x = pesticides, y = 2000, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_Pest_BenN
```

## Country x Plastic usage
```{r}
model_NB_country_plastic <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ Plasticyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_country_plastic)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_country_plastic)
```

```{r}
em_plastic_country <- emmeans(model_NB_country_plastic, pairwise ~ Plasticyesno * Country, adjust = "sidak")
em_plastic_country

cld_em_plastic_country <- cld(em_plastic_country, Letters = letters, adjust = "sidak")
print(cld_em_plastic_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot

Boxplot_plastic_country <- ggplot(MAP_BenN, aes(x = Plasticyesno, y = log_Total_onlymacro_plastic, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_plastic_country, aes(x = Plasticyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Plastic usage", y = "Log10 Plastic counts/Hectare") 
Boxplot_plastic_country
```
**Barplot - Log**

```{r}
summary_data_Plastic <- MAP_BenN %>%
  group_by(Country, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_Plastic_BenN <- ggplot(summary_data_Plastic, aes(x = Plasticyesno, y = mean_plastic)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_plastic_country, aes(x = Plasticyesno, y = 3.1, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of Mean Plastic Counts/Ha", x = "Plastic Treatment") +
  theme_publish()
barplot_Plastic_BenN
```
**Barplot**
```{r}
summary_data_Pest <- MAP_BenN %>%
  group_by(Country, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(Total_onlymacro_plastics, na.rm = TRUE),
    se_plastic = sd(Total_onlymacro_plastics, na.rm = TRUE) / sqrt(n())
  )

barplot_Plastic_BenN <- ggplot(summary_data_Pest, aes(x = Plasticyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_plastic_country, aes(x = Plasticyesno, y = 4000, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean Plastic Counts/Ha", x = "Plastic Treatment") +
  theme_publish()
barplot_Plastic_BenN
```



##ggsave Fieldmanagement x country
```{r}
plot_barplot_fieldcountry <- ((barplot_compost_BenN + barplot_Manure_BenN) / (barplot_Irri_BenN + barplot_Pest_BenN)/barplot_Plastic_BenN) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_fieldmanagementcountry_withoutlog.pdf", width = 10, height = 12, dpi = 600)
```


# A2 / A17 / A21 /A5/ A6
We want to know if certain categories are more prevalent with a certain field management (Compost, Manure, pesticides, Irrigation)
A2 sheets
A17 hard plastics
A21 stickers
A5 and A6 touwen 

columns to integers
```{r}
MAP_BenN[2:53] <- lapply(MAP_BenN[2:53], as.integer)
MAP_BenN[109] <- lapply(MAP_BenN[109], as.integer)

```

## Compost
### A2 - combi compost
```{r}
model_NB_compost_A2 <- glm.nb(
  formula = A2 ~ Compost * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_compost_A2)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_compost_A2)
```
```{r}
em_A2_country <- emmeans(model_NB_compost_A2, pairwise ~ Compost  * Country, adjust = "sidak")
em_A2_country

cld_em_A2_country <- cld(em_A2_country, Letters = letters, adjust = "sidak")
print(cld_em_A2_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A2, na.rm = TRUE) * 1.1

#the plot

Boxplot_A2_compost <- ggplot(MAP_BenN, aes(x = Compost, y = log_A2, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A2_country, aes(x = Compost, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Compost usage", y = "A2 counts/Hectare") 
Boxplot_A2_compost
```
```{r}
summary_data_A2 <- MAP_BenN %>%
  group_by(Country, Compost) %>%
  summarise(
    mean_plastic = mean(A2, na.rm = TRUE),
    se_plastic = sd(A2, na.rm = TRUE) / sqrt(n())
  )

barplot_A2_BenN <- ggplot(summary_data_A2, aes(x = Compost, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A2_country, aes(x = Compost, y = 1250, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean sheets (A2) Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_A2_BenN
```

### A17 - combi compost

```{r}
model_NB_compost_A17 <- glm.nb(
  formula = A17 ~ Compost * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_compost_A17)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_compost_A17)
```

```{r}
em_A17_country <- emmeans(model_NB_compost_A17, pairwise ~ Compost  * Country, adjust = "sidak")
em_A17_country

cld_em_A17_country <- cld(em_A17_country, Letters = letters, adjust = "sidak")
print(cld_em_A17_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A17, na.rm = TRUE) * 1.1

#the plot

Boxplot_A17_compost <- ggplot(MAP_BenN, aes(x = Compost, y = log_A17, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A17_country, aes(x = Compost, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Compost usage", y = "A17 counts/Hectare") 
Boxplot_A17_compost
```
```{r}
summary_data_A17 <- MAP_BenN %>%
  group_by(Country, Compost) %>%
  summarise(
    mean_plastic = mean(A17, na.rm = TRUE),
    se_plastic = sd(A17, na.rm = TRUE) / sqrt(n())
  )

barplot_A17_BenN <- ggplot(summary_data_A17, aes(x = Compost, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A17_country, aes(x = Compost, y = 600, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean hard plastics (A17) Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_A17_BenN
```

### A21 - combi compost
```{r}
model_NB_compost_A21 <- glm.nb(
  formula = A21 ~ Compost * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_compost_A21)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_compost_A21)
```

```{r}
em_A21_country <- emmeans(model_NB_compost_A21, pairwise ~ Compost  * Country, adjust = "sidak")
em_A21_country

cld_em_A21_country <- cld(em_A21_country, Letters = letters, adjust = "sidak")
print(cld_em_A21_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A21, na.rm = TRUE) * 1.1

#the plot

Boxplot_A21_compost <- ggplot(MAP_BenN, aes(x = Compost, y = log_A21, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A21_country, aes(x = Compost, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Compost usage", y = "Log10 A21 counts/Hectare") 
Boxplot_A21_compost
```
```{r}
summary_data_A21 <- MAP_BenN %>%
  group_by(Country, Compost) %>%
  summarise(
    mean_plastic = mean(A21, na.rm = TRUE),
    se_plastic = sd(A21, na.rm = TRUE) / sqrt(n())
  )

barplot_A21_BenN <- ggplot(summary_data_A21, aes(x = Compost, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A21_country, aes(x = Compost, y = 30, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean plastic stickers (A21) Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_A21_BenN
```


### A5 and A6 - combi compost
```{r}
model_NB_compost_A5A6 <- glm.nb(
  formula = A5_A6 ~ Compost * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_compost_A5A6)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_compost_A5A6)
```

```{r}
em_A5A6_country <- emmeans(model_NB_compost_A5A6, pairwise ~ Compost  * Country, adjust = "sidak")
em_A5A6_country

cld_em_A5A6_country <- cld(em_A5A6_country, Letters = letters, adjust = "sidak")
print(cld_em_A5A6_country)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A5A6, na.rm = TRUE) * 1.1

#the plot

Boxplot_A5A6_compost <- ggplot(MAP_BenN, aes(x = Compost, y = log_A5A6, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A5A6_country, aes(x = Compost, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Compost usage", y = "Log10 fibers (A5_A6) counts/Hectare") 
Boxplot_A5A6_compost
```
```{r}
summary_data_A5A6 <- MAP_BenN %>%
  group_by(Country, Compost) %>%
  summarise(
    mean_plastic = mean(A5_A6, na.rm = TRUE),
    se_plastic = sd(A5_A6, na.rm = TRUE) / sqrt(n())
  )

barplot_A5A6_BenN <- ggplot(summary_data_A5A6, aes(x = Compost, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A5A6_country, aes(x = Compost, y = 40, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean fibers (A5_A6) Counts/Ha", x = "Compost Treatment") +
  theme_publish()
barplot_A5A6_BenN
```

## Manure
### A2 - combi manure
```{r}
model_NB_manure_A2 <- glm.nb(
  formula = A2 ~ Manure * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_manure_A2)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_manure_A2)
```
```{r}
em_A2_country_manure <- emmeans(model_NB_manure_A2, pairwise ~ Manure  * Country, adjust = "sidak")
em_A2_country_manure

cld_em_A2_country_manure <- cld(em_A2_country_manure, Letters = letters, adjust = "sidak")
print(cld_em_A2_country_manure)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A2, na.rm = TRUE) * 1.1

#the plot

Boxplot_A2_manure <- ggplot(MAP_BenN, aes(x = Manure, y = log_A2, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A2_country_manure, aes(x = Manure, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Manure usage", y = "A2 counts/Hectare") 
Boxplot_A2_manure
```
```{r}
summary_data_A2 <- MAP_BenN %>%
  group_by(Country, Manure) %>%
  summarise(
    mean_plastic = mean(A2, na.rm = TRUE),
    se_plastic = sd(A2, na.rm = TRUE) / sqrt(n())
  )

barplot_A2_BenN_manure <- ggplot(summary_data_A2, aes(x = Manure, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A2_country_manure, aes(x = Manure, y = 1250, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean sheets (A2) Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_A2_BenN_manure
```

### A17 - combi Manure

```{r}
model_NB_Manure_A17 <- glm.nb(
  formula = A17 ~ Manure * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_Manure_A17)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_Manure_A17)
```

```{r}
em_A17_country_manure <- emmeans(model_NB_Manure_A17, pairwise ~ Manure  * Country, adjust = "sidak")
em_A17_country_manure

cld_em_A17_country_manure <- cld(em_A17_country_manure, Letters = letters, adjust = "sidak")
print(cld_em_A17_country_manure)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A17, na.rm = TRUE) * 1.1

#the plot

Boxplot_A17_manure <- ggplot(MAP_BenN, aes(x = Manure, y = log_A17, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A17_country_manure, aes(x = Manure, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Manure usage", y = "A17 counts/Hectare") 
Boxplot_A17_manure
```
```{r}
summary_data_A17 <- MAP_BenN %>%
  group_by(Country, Manure) %>%
  summarise(
    mean_plastic = mean(A17, na.rm = TRUE),
    se_plastic = sd(A17, na.rm = TRUE) / sqrt(n())
  )

barplot_A17_BenN_manure <- ggplot(summary_data_A17, aes(x = Manure, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A17_country_manure, aes(x = Manure, y = 600, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean hard plastcis (A17) Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_A17_BenN_manure
```

### A21 - combi Manure
```{r}
model_NB_Manure_A21 <- glm.nb(
  formula = A21 ~ Manure * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_Manure_A21)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_Manure_A21)
```

```{r}
em_A21_country_manure <- emmeans(model_NB_Manure_A21, pairwise ~ Manure  * Country, adjust = "sidak")
em_A21_country_manure

cld_em_A21_country_manure <- cld(em_A21_country_manure, Letters = letters, adjust = "sidak")
print(cld_em_A21_country_manure)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A21, na.rm = TRUE) * 1.1

#the plot

Boxplot_A21_Manure <- ggplot(MAP_BenN, aes(x = Manure, y = log_A21, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A21_country_manure, aes(x = Manure, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Manure usage", y = "Log10 A21 counts/Hectare") 
Boxplot_A21_Manure
```
```{r}
summary_data_A21 <- MAP_BenN %>%
  group_by(Country, Manure) %>%
  summarise(
    mean_plastic = mean(A21, na.rm = TRUE),
    se_plastic = sd(A21, na.rm = TRUE) / sqrt(n())
  )

barplot_A21_BenN_manure <- ggplot(summary_data_A21, aes(x = Manure, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A21_country_manure, aes(x = Manure, y = 30, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean plastic stickers (A21) Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_A21_BenN_manure
```


### A5 and A6 - combi Manure
```{r}
model_NB_Manure_A5A6 <- glm.nb(
  formula = A5_A6 ~ Manure * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_Manure_A5A6)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_Manure_A5A6)
```

```{r}
em_A5A6_country_Manure <- emmeans(model_NB_Manure_A5A6, pairwise ~ Manure  * Country, adjust = "sidak")
em_A5A6_country_Manure

cld_em_A5A6_country_Manure <- cld(em_A5A6_country_Manure, Letters = letters, adjust = "sidak")
print(cld_em_A5A6_country_Manure)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A5A6, na.rm = TRUE) * 1.1

#the plot

Boxplot_A5A6_Manure <- ggplot(MAP_BenN, aes(x = Manure, y = log_A5A6, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A5A6_country_Manure, aes(x = Manure, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Manure usage", y = "Log10 fibers (A5_A6) counts/Hectare") 
Boxplot_A5A6_Manure
```
```{r}
summary_data_A5A6 <- MAP_BenN %>%
  group_by(Country, Manure) %>%
  summarise(
    mean_plastic = mean(A5_A6, na.rm = TRUE),
    se_plastic = sd(A5_A6, na.rm = TRUE) / sqrt(n())
  )

barplot_A5A6_BenN_Manure <- ggplot(summary_data_A5A6, aes(x = Manure, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A5A6_country_Manure, aes(x = Manure, y = 90, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean fibers (A5_A6) Counts/Ha", x = "Manure Treatment") +
  theme_publish()
barplot_A5A6_BenN_Manure
```

## Pesticides
### A2 - Combi pesticides

```{r}
model_NB_pest_A2 <- glm.nb(
  formula = A2 ~ pesticides * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_pest_A2)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_pest_A2)
```
```{r}
em_A2_country_pest <- emmeans(model_NB_pest_A2, pairwise ~ pesticides  * Country, adjust = "sidak")
em_A2_country_pest

cld_em_A2_country_pest <- cld(em_A2_country_pest, Letters = letters, adjust = "sidak")
print(cld_em_A2_country_pest)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A2, na.rm = TRUE) * 1.1

#the plot

Boxplot_A2_pest <- ggplot(MAP_BenN, aes(x = pesticides, y = log_A2, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A2_country_pest, aes(x = pesticides, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "A2 counts/Hectare") 
Boxplot_A2_pest
```
```{r}
summary_data_A2 <- MAP_BenN %>%
  group_by(Country, pesticides) %>%
  summarise(
    mean_plastic = mean(A2, na.rm = TRUE),
    se_plastic = sd(A2, na.rm = TRUE) / sqrt(n())
  )

barplot_A2_BenN_pest <- ggplot(summary_data_A2, aes(x = pesticides, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A2_country_pest, aes(x = pesticides, y = 1250, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean sheets (A2) Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_A2_BenN_pest
```

### A17 - combi Pesticides

```{r}
model_NB_pest_A17 <- glm.nb(
  formula = A17 ~ pesticides * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_pest_A17)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_pest_A17)
```

```{r}
em_A17_country_pest <- emmeans(model_NB_pest_A17, pairwise ~ pesticides  * Country, adjust = "sidak")
em_A17_country_pest

cld_em_A17_country_pest <- cld(em_A17_country_pest, Letters = letters, adjust = "sidak")
print(cld_em_A17_country_pest)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A17, na.rm = TRUE) * 1.1

#the plot

Boxplot_A17_pest <- ggplot(MAP_BenN, aes(x = pesticides, y = log_A17, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A17_country_pest, aes(x = pesticides, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "A17 counts/Hectare") 
Boxplot_A17_pest
```
```{r}
summary_data_A17 <- MAP_BenN %>%
  group_by(Country, pesticides) %>%
  summarise(
    mean_plastic = mean(A17, na.rm = TRUE),
    se_plastic = sd(A17, na.rm = TRUE) / sqrt(n())
  )

barplot_A17_BenN_pest <- ggplot(summary_data_A17, aes(x = pesticides, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A17_country_pest, aes(x = pesticides, y = 600, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean hard plsatics (A17) Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_A17_BenN_pest
```

### A21 - combi pesticides
```{r}
model_NB_pest_A21 <- glm.nb(
  formula = A21 ~ pesticides * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_pest_A21)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_pest_A21)
```

```{r}
em_A21_country_pest <- emmeans(model_NB_pest_A21, pairwise ~ pesticides  * Country, adjust = "sidak")
em_A21_country_pest

cld_em_A21_country_pest <- cld(em_A21_country_pest, Letters = letters, adjust = "sidak")
print(cld_em_A21_country_pest)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A21, na.rm = TRUE) * 1.1

#the plot

Boxplot_A21_pest <- ggplot(MAP_BenN, aes(x = pesticides, y = log_A21, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A21_country_pest, aes(x = pesticides, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "Log10 A21 counts/Hectare") 
Boxplot_A21_pest
```
```{r}
summary_data_A21 <- MAP_BenN %>%
  group_by(Country, pesticides) %>%
  summarise(
    mean_plastic = mean(A21, na.rm = TRUE),
    se_plastic = sd(A21, na.rm = TRUE) / sqrt(n())
  )

barplot_A21_BenN_pest <- ggplot(summary_data_A21, aes(x = pesticides, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A21_country_pest, aes(x = pesticides, y = 40, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean plastic stickers (A21) Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_A21_BenN_pest
```


### A5 and A6 - combi Pesticides
```{r}
model_NB_pest_A5A6 <- glm.nb(
  formula = A5_A6 ~ pesticides * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_pest_A5A6)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_pest_A5A6)
```

```{r}
em_A5A6_country_pest <- emmeans(model_NB_pest_A5A6, pairwise ~ pesticides  * Country, adjust = "sidak")
em_A5A6_country_pest

cld_em_A5A6_country_pest <- cld(em_A5A6_country_pest, Letters = letters, adjust = "sidak")
print(cld_em_A5A6_country_pest)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A5A6, na.rm = TRUE) * 1.1
#the plot

Boxplot_A5A6_pest <- ggplot(MAP_BenN, aes(x = pesticides, y = log_A5A6, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A5A6_country_pest, aes(x = pesticides, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Pesticides usage", y = "Log10 fibers (A5_A6) counts/Hectare") 
Boxplot_A5A6_pest
```
```{r}
summary_data_A5A6 <- MAP_BenN %>%
  group_by(Country, pesticides) %>%
  summarise(
    mean_plastic = mean(A5_A6, na.rm = TRUE),
    se_plastic = sd(A5_A6, na.rm = TRUE) / sqrt(n())
  )

barplot_A5A6_BenN_pest <- ggplot(summary_data_A5A6, aes(x = pesticides, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A5A6_country_pest, aes(x = pesticides, y = 120, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean fibers (A5_A6) Counts/Ha", x = "Pesticides Treatment") +
  theme_publish()
barplot_A5A6_BenN_pest
```
## Irrigation
### A2 - Combi irrigation

```{r}
model_NB_irri_A2 <- glm.nb(
  formula = A2 ~ Irrigationyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_irri_A2)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_irri_A2)
```
```{r}
em_A2_country_irri <- emmeans(model_NB_irri_A2, pairwise ~ Irrigationyesno  * Country, adjust = "sidak")
em_A2_country_irri

cld_em_A2_country_irri <- cld(em_A2_country_irri, Letters = letters, adjust = "sidak")
print(cld_em_A2_country_irri)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A2, na.rm = TRUE) * 1.1

#the plot

Boxplot_A2_irri <- ggplot(MAP_BenN, aes(x = Irrigationyesno, y = log_A2, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A2_country_irri, aes(x = Irrigationyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Irrigation usage", y = "A2 counts/Hectare") 
Boxplot_A2_irri
```
```{r}
summary_data_A2 <- MAP_BenN %>%
  group_by(Country, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(A2, na.rm = TRUE),
    se_plastic = sd(A2, na.rm = TRUE) / sqrt(n())
  )

barplot_A2_BenN_irri <- ggplot(summary_data_A2, aes(x = Irrigationyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A2_country_irri, aes(x = Irrigationyesno, y = 1250, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean sheets (A2) Counts/Ha", x = "Irrigation Treatment") +
  theme_publish()
barplot_A2_BenN_irri
```

### A17 - combi irrigation

```{r}
model_NB_irri_A17 <- glm.nb(
  formula = A17 ~ Irrigationyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_irri_A17)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_irri_A17)
```

```{r}
em_A17_country_irri <- emmeans(model_NB_irri_A17, pairwise ~ Irrigationyesno  * Country, adjust = "sidak")
em_A17_country_irri

cld_em_A17_country_irri <- cld(em_A17_country_irri, Letters = letters, adjust = "sidak")
print(cld_em_A17_country_irri)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A17, na.rm = TRUE) * 1.1

#the plot

Boxplot_A17_irri <- ggplot(MAP_BenN, aes(x = Irrigationyesno, y = log_A17, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A17_country_irri, aes(x = Irrigationyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Irrigation usage", y = "A17 counts/Hectare") 
Boxplot_A17_irri
```
```{r}
summary_data_A17 <- MAP_BenN %>%
  group_by(Country, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(A17, na.rm = TRUE),
    se_plastic = sd(A17, na.rm = TRUE) / sqrt(n())
  )

barplot_A17_BenN_irri <- ggplot(summary_data_A17, aes(x = Irrigationyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A17_country_irri, aes(x = Irrigationyesno, y = 600, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean hard plastics (A17) Counts/Ha", x = "Irrigation Treatment") +
  theme_publish()
barplot_A17_BenN_irri
```

### A21 - combi irrigation
```{r}
model_NB_irri_A21 <- glm.nb(
  formula = A21 ~ Irrigationyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_irri_A21)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_irri_A21)
```

```{r}
em_A21_country_irri <- emmeans(model_NB_irri_A21, pairwise ~ Irrigationyesno  * Country, adjust = "sidak")
em_A21_country_irri

em_A21_country_irri <- cld(em_A21_country_irri, Letters = letters, adjust = "sidak")
print(em_A21_country_irri)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A21, na.rm = TRUE) * 1.1

#the plot

Boxplot_A21_irri <- ggplot(MAP_BenN, aes(x = Irrigationyesno, y = log_A21, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = em_A21_country_irri, aes(x = Irrigationyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Irrigation usage", y = "Log10 A21 counts/Hectare") 
Boxplot_A21_irri
```
```{r}
summary_data_A21 <- MAP_BenN %>%
  group_by(Country, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(A21, na.rm = TRUE),
    se_plastic = sd(A21, na.rm = TRUE) / sqrt(n())
  )

barplot_A21_BenN_irri <- ggplot(summary_data_A21, aes(x = Irrigationyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = em_A21_country_irri, aes(x = Irrigationyesno, y = 40, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean plastic stickers (A21) Counts/Ha", x = "Irrigation Treatment") +
  theme_publish()
barplot_A21_BenN_irri
```


### A5 and A6 - combi irrigation
```{r}
model_NB_irri_A5A6 <- glm.nb(
  formula = A5_A6 ~ Irrigationyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_irri_A5A6)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_irri_A5A6)
```

```{r}
em_A5A6_country_irri <- emmeans(model_NB_irri_A5A6, pairwise ~ Irrigationyesno  * Country, adjust = "sidak")
em_A5A6_country_irri

cld_em_A5A6_country_irri <- cld(em_A5A6_country_irri, Letters = letters, adjust = "sidak")
print(cld_em_A5A6_country_irri)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A5A6, na.rm = TRUE) * 1.1

#the plot

Boxplot_A5A6_irri <- ggplot(MAP_BenN, aes(x = Irrigationyesno, y = log_A5A6, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A5A6_country_irri, aes(x = Irrigationyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Irrigation usage", y = "Log10 fibers (A5_A6) counts/Hectare") 
Boxplot_A5A6_irri
```
```{r}
summary_data_A5A6 <- MAP_BenN %>%
  group_by(Country, Irrigationyesno) %>%
  summarise(
    mean_plastic = mean(A5_A6, na.rm = TRUE),
    se_plastic = sd(A5_A6, na.rm = TRUE) / sqrt(n())
  )

barplot_A5A6_BenN_irri <- ggplot(summary_data_A5A6, aes(x = Irrigationyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A5A6_country_irri, aes(x = Irrigationyesno, y = 45, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean fibers (A5_A6) Counts/Ha", x = "Irrigation Treatment") +
  theme_publish()
barplot_A5A6_BenN_irri
```

## Plastic usage

###A2 - combi plastic

```{r}
model_NB_plastic_A2 <- glm.nb(
  formula = A2 ~ Plasticyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_plastic_A2)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_plastic_A2)
```

```{r}
em_A2_country_plastic <- emmeans(model_NB_plastic_A2, pairwise ~ Plasticyesno  * Country, adjust = "sidak")
em_A2_country_plastic

cld_em_A2_country_plastic <- cld(em_A2_country_plastic, Letters = letters, adjust = "sidak")
print(cld_em_A2_country_plastic)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A2, na.rm = TRUE) * 1.1

#the plot

Boxplot_A2_plastic <- ggplot(MAP_BenN, aes(x = Plasticyesno, y = log_A2, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A2_country_plastic, aes(x = Plasticyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Plastic usage", y = "Log10 sheets (A2) counts/Hectare") 
Boxplot_A2_plastic
```
```{r}
summary_data_A2 <- MAP_BenN %>%
  group_by(Country, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(A2, na.rm = TRUE),
    se_plastic = sd(A2, na.rm = TRUE) / sqrt(n())
  )

barplot_A2_BenN_plastic <- ggplot(summary_data_A2, aes(x = Plasticyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A2_country_plastic, aes(x = Plasticyesno, y = 2500, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean sheets (A2) Counts/Ha", x = "Plastic Treatment") +
  theme_publish()
barplot_A2_BenN_plastic
```

### A17 - combi plastic
```{r}
model_NB_plastic_A17 <- glm.nb(
  formula = A17 ~ Plasticyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_plastic_A17)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_plastic_A17)
```

```{r}
em_A17_country_plastic <- emmeans(model_NB_plastic_A17, pairwise ~ Plasticyesno  * Country, adjust = "sidak")
em_A17_country_plastic

cld_em_A17_country_plastic <- cld(em_A17_country_plastic, Letters = letters, adjust = "sidak")
print(cld_em_A17_country_plastic)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A17, na.rm = TRUE) * 1.1

#the plot

Boxplot_A17_plastic <- ggplot(MAP_BenN, aes(x = Plasticyesno, y = log_A17, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A17_country_plastic, aes(x = Plasticyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Plastic usage", y = "Log10 hard plastics (A17) counts/Hectare") 
Boxplot_A17_plastic
```
```{r}
summary_data_A17 <- MAP_BenN %>%
  group_by(Country, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(A17, na.rm = TRUE),
    se_plastic = sd(A17, na.rm = TRUE) / sqrt(n())
  )

barplot_A17_BenN_plastic <- ggplot(summary_data_A17, aes(x = Plasticyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A17_country_plastic, aes(x = Plasticyesno, y = 1250, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean hard plastics (A17) Counts/Ha", x = "Plastic Treatment") +
  theme_publish()
barplot_A17_BenN_plastic
```

### A21 - combi plastic
```{r}
model_NB_plastic_A21 <- glm.nb(
  formula = A21 ~ Plasticyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_plastic_A21)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_plastic_A21)
```

```{r}
em_A21_country_plastic <- emmeans(model_NB_plastic_A21, pairwise ~ Plasticyesno  * Country, adjust = "sidak")
em_A21_country_plastic

cld_em_A21_country_plastic <- cld(em_A21_country_plastic, Letters = letters, adjust = "sidak")
print(cld_em_A21_country_plastic)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A21, na.rm = TRUE) * 1.1

#the plot

Boxplot_A21_plastic <- ggplot(MAP_BenN, aes(x = Plasticyesno, y = log_A21, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A21_country_plastic, aes(x = Plasticyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Plastic usage", y = "Log10 plastic stickers (A21) counts/Hectare") 
Boxplot_A21_plastic
```
```{r}
summary_data_A21 <- MAP_BenN %>%
  group_by(Country, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(A21, na.rm = TRUE),
    se_plastic = sd(A21, na.rm = TRUE) / sqrt(n())
  )

barplot_A21_BenN_plastic <- ggplot(summary_data_A21, aes(x = Plasticyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A21_country_plastic, aes(x = Plasticyesno, y = 30, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean plastic stickers (A21) Counts/Ha", x = "Plastic Treatment") +
  theme_publish()
barplot_A21_BenN_plastic
```


### A5_A6 - combi plastic

```{r}
model_NB_plastic_A5A6 <- glm.nb(
  formula = A5_A6 ~ Plasticyesno * Country, 
  offset(log(Surface_m2)), 
  data = MAP_BenN, 
  control = glm.control(maxit = 100))
    
summary(model_NB_plastic_A5A6)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_plastic_A5A6)
```

```{r}
em_A5A6_country_plastic <- emmeans(model_NB_plastic_A5A6, pairwise ~ Plasticyesno  * Country, adjust = "sidak")
em_A5A6_country_plastic

cld_em_A5A6_country_plastic <- cld(em_A5A6_country_plastic, Letters = letters, adjust = "sidak")
print(cld_em_A5A6_country_plastic)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_BenN$log_A5A6, na.rm = TRUE) * 1.1

#the plot

Boxplot_A5A6_plastic <- ggplot(MAP_BenN, aes(x = Plasticyesno, y = log_A5A6, fill = Country)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  facet_wrap(~ Country) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_A5A6_country_plastic, aes(x = Plasticyesno, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Plastic usage", y = "Log10 fibers (A5_A6) counts/Hectare") 
Boxplot_A5A6_plastic
```
```{r}
summary_data_A5A6 <- MAP_BenN %>%
  group_by(Country, Plasticyesno) %>%
  summarise(
    mean_plastic = mean(A5_A6, na.rm = TRUE),
    se_plastic = sd(A5_A6, na.rm = TRUE) / sqrt(n())
  )

barplot_A5A6_BenN_plastic <- ggplot(summary_data_A5A6, aes(x = Plasticyesno, y = mean_plastic, fill = Country)) +
  facet_wrap(~ Country) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_A5A6_country_plastic, aes(x = Plasticyesno, y = 150, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Mean fibers (A5_A6) Counts/Ha", x = "Plastic Treatment") +
  theme_publish()
barplot_A5A6_BenN_plastic
```

##ggsave
###A2
```{r}
plot_barplot_A2 <- ((barplot_A2_BenN + barplot_A2_BenN_manure + barplot_A2_BenN_plastic) / (barplot_A2_BenN_pest + barplot_A2_BenN_irri) ) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_A2.png", width = 15, height = 12, dpi = 600)
```
###A17
```{r}
plot_barplot_A17 <- ((barplot_A17_BenN + barplot_A17_BenN_manure + barplot_A17_BenN_plastic) / (barplot_A17_BenN_pest + barplot_A17_BenN_irri) ) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_A17.png", width = 15, height = 12, dpi = 600)
```
###A21
```{r}
plot_barplot_A21 <- ((barplot_A21_BenN + barplot_A21_BenN_manure + barplot_A21_BenN_plastic) / (barplot_A21_BenN_pest + barplot_A21_BenN_irri) ) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_A21.png", width = 15, height = 12, dpi = 600)
```

###A5A6

```{r}
plot_barplot_A5A6 <- ((barplot_A5A6_BenN + barplot_A5A6_BenN_Manure + barplot_A5A6_BenN_plastic) / (barplot_A5A6_BenN_pest + barplot_A5A6_BenN_irri) ) + plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = "A")
 
ggsave("plot_barplot_A5A6.png", width = 15, height = 12, dpi = 600)
```

# Distance for Belgium
## NB model
```{r}
model_NB_distance <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ distance_city + Distance_primroutes + distance_highway + min_distance_IndorW + distance_village, 
  offset(log(Surface_m2)), 
  data = MAP_Belgium_noNA, 
  control = glm.control(maxit = 100))
    
summary(model_NB_distance)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_distance)
```

```{r}
model_NB_distance_1 <- glm.nb(
  formula = Total_onlymacro_plastics_count ~ min_city_village + Distance_primroutes + distance_highway + min_distance_IndorW, 
  offset(log(Surface_m2)), 
  data = MAP_Belgium_noNA, 
  control = glm.control(maxit = 100))
    
summary(model_NB_distance_1)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_distance_1)
```

## Distance city
Make a correlation plot to know the correlation between the amount of plastics and the distance to the city
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_Total_onlymacro_plastic, MAP_Belgium_noNA$distance_city)
pred <- predict(model_NB_distance, type = "response")
# Plot
cor_plot_distance_city <- ggplot(MAP_Belgium_noNA, aes(x = distance_city, y = log_Total_onlymacro_plastic)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance$theta)),
    se = TRUE) +
  labs(
    x = "Distance to city (m)",
    y = "Log total plastic/Ha"
  ) +
  theme_publish()
cor_plot_distance_city
```
## Correlation Distance_primroutes

```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_Total_onlymacro_plastic, MAP_Belgium_noNA$Distance_primroutes)
pred <- predict(model_NB_distance, type = "response")
# Plot
cor_plot_distance_primroutes <- ggplot(MAP_Belgium_noNA, aes(x = Distance_primroutes, y = log_Total_onlymacro_plastic)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance$theta)),
    se = TRUE) +
   annotate(
    "text",
    x = Inf, y = Inf,
    label = paste("Correlation =", round(cor_value, 3)),
    hjust = 1.1, vjust = 1.5
  )+
  labs(
    x = "Distance to primair routes (m)",
    y = "Log total plastic/Ha"
  ) +
  theme_publish()
cor_plot_distance_primroutes
```
## Correlation distance_highway
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_Total_onlymacro_plastic, MAP_Belgium_noNA$distance_highway)
pred <- predict(model_NB_distance, type = "response")
# Plot
cor_plot_distance_highway <- ggplot(MAP_Belgium_noNA, aes(x = distance_highway, y = log_Total_onlymacro_plastic)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance$theta)),
    se = TRUE) +
  labs(
    #title = paste("Scatter plot with correlation =", round(cor_value, 3)),
    x = "Distance to highway (m)",
    y = "Log total plastic/Ha"
  ) +
  theme_publish()
cor_plot_distance_highway
```

## Correlation min_distance_IndorW
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_Total_onlymacro_plastic, MAP_Belgium_noNA$min_distance_IndorW)
pred <- predict(model_NB_distance, type = "response")
# Plot
cor_plot_distance_IndorW <- ggplot(MAP_Belgium_noNA, aes(x = min_distance_IndorW, y = log_Total_onlymacro_plastic)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance$theta)),
    se = TRUE) +
  labs(
    #title = paste("Scatter plot with correlation =", round(cor_value, 3)),
    x = "Distance to Industry or Waste recyling (m)",
    y = "Log total plastic/Ha"
  ) +
  theme_publish()
cor_plot_distance_IndorW
```
## Correlation distance_village
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_Total_onlymacro_plastic, MAP_Belgium_noNA$distance_village)
pred <- predict(model_NB_distance, type = "response")
# Plot
cor_plot_distance_Village <- ggplot(MAP_Belgium_noNA, aes(x = distance_village, y = log_Total_onlymacro_plastic)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance$theta)),
    se = TRUE) +
  labs(
    x = "Distance to villages (m)",
    y = "Log total plastic/Ha"
  ) +
  theme_publish()
cor_plot_distance_Village
```

## Correlation min_distance village and city
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_Total_onlymacro_plastic, MAP_Belgium_noNA$min_city_village)
pred <- predict(model_NB_distance_1, type = "response")
# Plot
cor_plot_distance_Village_city <- ggplot(MAP_Belgium_noNA, aes(x = min_city_village, y = log_Total_onlymacro_plastic)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_1$theta)),
    se = TRUE) +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste("Correlation =", round(cor_value, 3)),
    hjust = 1.1, vjust = 1.5
  )+
  labs(
    x = "Minimal distance to villages and city (m)",
    y = "Log total plastic/Ha"
  ) +
  theme_publish()
cor_plot_distance_Village_city
```


#A2/A17/A20
we want to know if a specific category is more correlated with the category A2 or A17 or A20

```{r}
MAP_Belgium_noNA[2:53] <- lapply(MAP_Belgium_noNA[2:53], as.integer)
```

## A2


```{r}
model_NB_distance_A2 <- glm.nb(
  formula = A2 ~ distance_city + Distance_primroutes + distance_highway + min_distance_IndorW + distance_village, 
  offset(log(Surface_m2)), 
  data = MAP_Belgium_noNA, 
  control = glm.control(maxit = 100)
)
summary(model_NB_distance_A2)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_distance_A2)


summary(MAP_Belgium_noNA$A2)


```

### Distance city
### Primroutes
### Highways
### Minimum distance Recyclage or industry
### Distance villages

## A17
```{r}
model_NB_distance_A17 <- glm.nb(
  formula = A17 ~ distance_city + Distance_primroutes + distance_highway + min_distance_IndorW + distance_village, 
  offset(log(Surface_m2)), 
  data = MAP_Belgium_noNA, 
  control = glm.control(maxit = 100)
)
summary(model_NB_distance_A17)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_distance_A17)
```
### Distance city
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A17, MAP_Belgium_noNA$distance_city)
pred <- predict(model_NB_distance_A17, type = "response")
# Plot
cor_plot_distance_city <- ggplot(MAP_Belgium_noNA, aes(x = distance_city, y = log_A17)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A17$theta)),
    se = TRUE) +
  labs(
    x = "Distance to city (m)",
    y = "Log hard plastics (A17)/Ha"
  ) +
  theme_publish()
cor_plot_distance_city
```

### Primroutes

```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A17, MAP_Belgium_noNA$Distance_primroutes)
pred <- predict(model_NB_distance_A17, type = "response")
# Plot
cor_plot_distance_primroutes_A17 <- ggplot(MAP_Belgium_noNA, aes(x = Distance_primroutes, y = log_A17)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A17$theta)),
    se = TRUE) +
  labs(
    x = "Distance to primair routes (m)",
    y = "Log hard plastic (A17)/Ha"
  ) +
  theme_publish()
cor_plot_distance_primroutes_A17
```
### Highways

```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A17, MAP_Belgium_noNA$distance_highway)
pred <- predict(model_NB_distance_A17, type = "response")
# Plot
cor_plot_distance_highway_A17 <- ggplot(MAP_Belgium_noNA, aes(x = distance_highway, y = log_A17)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A17$theta)),
    se = TRUE) +
  labs(
    #title = paste("Scatter plot with correlation =", round(cor_value, 3)),
    x = "Distance to highway (m)",
    y = "Log hard plastic (A17)/Ha"
  ) +
  theme_publish()
cor_plot_distance_highway_A17
```
### Minimum distance Recyclage or industry
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A17, MAP_Belgium_noNA$min_distance_IndorW)
pred <- predict(model_NB_distance_A17, type = "response")
# Plot
cor_plot_distance_IndorW <- ggplot(MAP_Belgium_noNA, aes(x = min_distance_IndorW, y = log_A17)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A17$theta)),
    se = TRUE) +
  labs(
    #title = paste("Scatter plot with correlation =", round(cor_value, 3)),
    x = "Distance to Industry or Waste recyling (m)",
    y = "Log hard plastic (A17)/Ha"
  ) +
  theme_publish()
cor_plot_distance_IndorW
```
### Distance villages
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A17, MAP_Belgium_noNA$distance_village)
pred <- predict(model_NB_distance_A17, type = "response")
# Plot
cor_plot_distance_Village_A17 <- ggplot(MAP_Belgium_noNA, aes(x = distance_village, y = log_A17)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A17$theta)),
    se = TRUE) +
  labs(
    x = "Distance to villages (m)",
    y = "Log hard plastic (A17)/Ha"
  ) +
  theme_publish()
cor_plot_distance_Village_A17
```
## A20

```{r}
model_NB_distance_A20 <- glm.nb(
  formula = A20 ~ distance_city + Distance_primroutes + distance_highway + min_distance_IndorW + distance_village, 
  offset(log(Surface_m2)), 
  data = MAP_Belgium_noNA, 
  control = glm.control(maxit = 100)
)
summary(model_NB_distance_A20)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_distance_A20)
```
### Distance city
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A20, MAP_Belgium_noNA$distance_city)
pred <- predict(model_NB_distance_A20, type = "response")
# Plot
cor_plot_distance_city_A20 <- ggplot(MAP_Belgium_noNA, aes(x = distance_city, y = log_A20)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A20$theta)),
    se = TRUE) +
  labs(
    x = "Distance to city (m)",
    y = "Log crisp packages (A20)/Ha"
  ) +
  theme_publish()
cor_plot_distance_city_A20
```
### Primroutes
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A20, MAP_Belgium_noNA$Distance_primroutes)
pred <- predict(model_NB_distance_A20, type = "response")
# Plot
cor_plot_distance_primroutes_A20 <- ggplot(MAP_Belgium_noNA, aes(x = Distance_primroutes, y = log_A20)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A20$theta)),
    se = TRUE) +
  labs(
    x = "Distance to primair routes (m)",
    y = "Log crisp packages (A20)/Ha"
  ) +
  theme_publish()
cor_plot_distance_primroutes_A20
```
### Highways
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A20, MAP_Belgium_noNA$distance_highway)
pred <- predict(model_NB_distance_A20, type = "response")
# Plot
cor_plot_distance_highway_A20 <- ggplot(MAP_Belgium_noNA, aes(x = distance_highway, y = log_A20)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A20$theta)),
    se = TRUE) +
  labs(
    #title = paste("Scatter plot with correlation =", round(cor_value, 3)),
    x = "Distance to highway (m)",
    y = "Log crisp package (A20)/Ha"
  ) +
  theme_publish()
cor_plot_distance_highway_A20
```

### Minimum distance Recyclage or industry
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A20, MAP_Belgium_noNA$min_distance_IndorW)
pred <- predict(model_NB_distance_A20, type = "response")
# Plot
cor_plot_distance_IndorW_A20 <- ggplot(MAP_Belgium_noNA, aes(x = min_distance_IndorW, y = log_A20)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A20$theta)),
    se = TRUE) +
  labs(
    #title = paste("Scatter plot with correlation =", round(cor_value, 3)),
    x = "Distance to Industry or Waste recyling (m)",
    y = "Log crisp package/Ha"
  ) +
  theme_publish()
cor_plot_distance_IndorW_A20
```

### Distance villages
```{r}
# Compute correlation
cor_value <- cor(MAP_Belgium_noNA$log_A20, MAP_Belgium_noNA$distance_village)
pred <- predict(model_NB_distance_A20, type = "response")
# Plot
cor_plot_distance_Village_A20 <- ggplot(MAP_Belgium_noNA, aes(x = distance_village, y = log_A20)) +
  geom_point(size = 2) +
  geom_smooth(
    method = "glm",
    method.args = list(family = negative.binomial(theta = model_NB_distance_A20$theta)),
    se = TRUE) +
  labs(
    x = "Distance to villages (m)",
    y = "Log crisp package (A20)/Ha"
  ) +
  theme_publish()
cor_plot_distance_Village_A20
```

# Bodemtextuur
```{r}
model_NB_bodemtextuur <- glm.nb(
  formula = Total_onlymacro_plastics ~ Soil_Texture, 
  offset(log(Surface_m2)), 
  data = MAP_all_noNA, 
  control = glm.control(maxit = 100)
)
summary(model_NB_bodemtextuur)
par(mfrow = c(2, 2))  # set up 4 plots on one screen
plot(model_NB_bodemtextuur)
```


```{r}
em_bodemtextuur <- emmeans(model_NB_bodemtextuur, ~ Soil_Texture, adjust = "sidak")
em_bodemtextuur

cld_em_bodemtextuur <- cld(em_bodemtextuur, Letters = letters, adjust = "sidak")
print(cld_em_bodemtextuur)

# Choose a fixed y-position slightly above the tallest value in the whole dataset
fixed_y <- max(MAP_all_noNA$log_Total_onlymacro_plastic, na.rm = TRUE) * 1.1

#the plot

Boxplot_bodemtextuur <- ggplot(MAP_all_noNA, aes(x = Soil_Texture, y = log_Total_onlymacro_plastic)) +
  geom_boxplot(outlier.shape = 2, width = 0.7) +
  geom_jitter(width = 0.3, alpha = 0.5) +
  #mean
  stat_summary(fun = mean, geom = "crossbar", color = "lightgrey", width = 0.69) +
  #significant letter
  geom_text(data = cld_em_bodemtextuur, aes(x = Soil_Texture, y = fixed_y, label = .group), inherit.aes = FALSE, fontface = "bold") +
  theme_publish() + 
  
  labs(title = "",
       x = "Soil texture", y = "log total plastics/Hectare") 
Boxplot_bodemtextuur
```
```{r}
summary_data_bodemtextuur <- MAP_all_noNA %>%
  group_by(Soil_Texture) %>%
  summarise(
    mean_plastic = mean(log_Total_onlymacro_plastic, na.rm = TRUE),
    se_plastic = sd(log_Total_onlymacro_plastic, na.rm = TRUE) / sqrt(n())
  )

barplot_bodemtextuur <- ggplot(summary_data_bodemtextuur, aes(x = Soil_Texture, y = mean_plastic)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_errorbar(aes(ymin = mean_plastic - se_plastic, ymax = mean_plastic + se_plastic),
                width = 0.2) +
  geom_text(data = cld_em_bodemtextuur, aes(x = Soil_Texture, y = 3, label = .group), inherit.aes = FALSE, fontface = "bold") +
  labs(y = "Log10 of mean total plastics/Ha", x = "Soil Texture") +
  theme_publish()
barplot_bodemtextuur
```


